---
title: "nullrangesData package"
output:
  rmarkdown::html_document
vignette: |
  %\VignetteIndexEntry{nullrangesData package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The *nullrangesData* package provides datasets for the *nullranges*
package vignette, in particular example datasets for exclusion
regions, DNase hypersensitivity sites (DHS), Single Cell Multiome ATAC and Gene Expression assay,
CTCF binding sites,
and CTCF genomic interactions.

```{r}
library(nullrangesData)
suppressPackageStartupMessages(library(GenomicRanges))
suppressPackageStartupMessages(library(InteractionSet))
```

A549 DHS peaks (see `?DHSA549Hg38` for details).

```{r}
dhs <- DHSA549Hg38()
dhs
```

Chromium Single Cell Multiome ATAC + Gene Expression assay. See corresponding man pages for details..

```{r}
data("sc_rna")
data("sc_promoter")
sc_rna
sc_promoter
```

CTCF binding sites, 10kb bins with CTCF and DHS peaks, and CTCF-bound
genomics interactions. See corresponding man pages for details.

```{r}
bins <- hg19_10kb_bins()
binPairs <- hg19_10kb_ctcfBoundBinPairs()
bins
binPairs
```

# Session information

```{r}
sessionInfo()
```
